%! Author = Len Washington III
%! Date = 8/21/2023

% Preamble
\documentclass[12pt]{report}

% Packages
\setcounter{chapter}{4}
\setcounter{section}{3}
\usepackage{math252homework}
\newcommand{\ivpsep}{\mbox{{ }{ }}}

% Document
\begin{document}

\customsection{4.3}{sec:4.3}

In Problems 1--14 find the general solution of the given second-order differential equation.
\begin{enumerate}[label=\arabic*.,start=3]
	\item \[ y'' - y' - 6y = 0 \]				% TODO: Problem 4.3 3
	\setcounter{enumi}{4}
	\item \[ y'' + 8y' + 16y = 0 \]				% TODO: Problem 4.3 5
	\item \[ y'' - 10y' + 25y = 0 \]			% TODO: Problem 4.3 6
	\setcounter{enumi}{8}
	\item \[ y'' + 9y = 0 \] 					% TODO: Problem 4.3 9
	\setcounter{enumi}{10}
	\item \[ y'' - 4y' + 5y = 0 \] 				% TODO: Problem 4.3 11
	\item \[ 2y'' + 2y' + y = 0 \] 				% TODO: Problem 4.3 12
\end{enumerate}

In Problems 15--28 find the general solution of the given higher-order differential equation.
\begin{enumerate}[label=\arabic*.,start=15]
	\item \[ y''' - 4y'' - 5y' = 0 \]										% TODO: Problem 4.3 15
	\setcounter{enumi}{16}
	\item \[ y''' - 5y'' + 3y' + 9y = 0 \]									% TODO: Problem 4.3 17
	\setcounter{enumi}{24}
	\item \[ 16\frac{d^{4}y}{dx^{4}} + 24\frac{d^{2}y}{dx^{2}} + 9y = 0 \]	% TODO: Problem 4.3 25
	\item \[ \frac{d^{4}y}{dx^{4}} - 7\frac{d^{2}y}{dx^{2}} - 18y = 0 \]	% TODO: Problem 4.3 26
\end{enumerate}

In Problems 29--36 solve the given initial-value problem.
\begin{enumerate}[label=\arabic*.,start=31]
	\item \[ \frac{d^{2}y}{dt^{2}} - 4\frac{dy}{dt} - 5y = 0,\ivpsep y(1)=0,\ivpsep y'(1)=2 \]			% TODO: Problem 4.3 31
	\item \[ 4y'' - 4y' - 3y = 0,\ivpsep y(0)=1,\ivpsep y'(0)=5 \]										% TODO: Problem 4.3 32
\end{enumerate}

In Problems 49--58 find a homogenous linear differential equation with constant coefficients whose general solution is given.
\begin{enumerate}[label=\arabic*.,start=49]
	\item \[ y = c_{1}e^{x} + c_{2}e^{5x} \]							% TODO: Problem 4.3 49
	\item \[ y = c_{1}e^{-4x} + c_{2}e^{-3x} \]							% TODO: Problem 4.3 50
	\setcounter{enumi}{52}
	\item \[ y = c_{1}\cos(3x) + c_{2}\sin(3x) \]						% TODO: Problem 4.3 53
	\setcounter{enumi}{55}
	\item \[ y = c_{1} + c_{2}e^{2x}\cos(5x) + c_{3}e^{2x}\sin(5x) \]	% TODO: Problem 4.3 56
\end{enumerate}

\customsection{4.1}{sec:4.1}

In Problems 23--30 verify that the given functions form a fundamental set of solutions of the differential equation on the indicated interval. Form the general solution.

\begin{enumerate}[label=\arabic*.,start=23]
    \item \[ y'' - y' - 12y = 0;\ivpsep e^{-3x},\ivpsep e^{4x},\ivpsep (-\infty, \infty) \]					% TODO: Problem 4.1 23
	\setcounter{enumi}{24}
	\item \[ y'' - 2y' + 5y = 0;\ivpsep e^{x}\cos(2x), \ivpsep e^{x}\sin(2x),\ivpsep (-\infty, \infty) \]	% TODO: Problem 4.1 25
\end{enumerate}

\begin{enumerate}[label=\arabic*.,start=40]
    \item Is the set of functions $f_{1}(x) = e^{x+2}, f_{2}(x) = e^{x-3}$ linearly dependent or linearly independent on $(-\infty, \infty)$? Discuss. % TODO: Problem 4.1 40
	\item Suppose $y_{1}$, $y_{2}$, $\dots$, $y_{k}$ are $k$ linearly independent solutions on $(-\infty, \infty)$ of a homogeneous linear $n$th-order differential equation with constant coefficients. By Theorem 4.1.2 it follows that $y_{k+1}=0$ is also a solution of the differential equation. Is the set of functions $y_{1}, y_{2}, \dots, y_{k}, y_{k+1}$ linearly dependent or linearly independent on $(-\infty, \infty)$? Discuss. % TODO: Problem 4.1 41
	\item Suppose that $y_{1}, y_{2}, \dots, y_{k}$ are $k$ nontrivial solutions of a homogeneous linear $n$th-order differential equation with constant coefficients and that $k=n+1$. Is the set of solutions $y_{1}, y_{2}, \dots, y_{k}$ linearly dependent or linearly independent on $(-\infty, \infty)$? Discuss. % TODO: Problem 4.1 42
\end{enumerate}

\end{document}